Sexual selection improves population fitness: a meta-analysis

### 2018-08-09 meta_analysis_sexual_selection_pop_fitness.Rmd
July Update 2
Former-commit-id: b36ca7cd53a41a1312d6526493c85c9fd656bf11

#Obtain Bayes Factor of likelihood that the outcome is greater than 0
BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
#Obtain BF for all components
Hypotheses <- list()
BFs <- list()
Hypotheses[["Behavioural Plasticity"]] <- hypothesis(components.brms, "Intercept > 0") #Intercept in model, need to do it by itself
BFs[["Behavioural Plasticity"]] <- Hypotheses[["Behavioural Plasticity"]][["hypothesis"]][["Evid.Ratio"]]
for (i in BF.outcome.list){
Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome",i," > 0", sep = ""))
BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
} #Loop for all fitness compoinents
fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```

>>>>

#Obtain Bayes Factor of likelihood that the outcome is greater than 0
BF.outcome.list <-  c('Body Size', 'Development Rate', 'Early Fecundity', 'Immunity', 'Mating Duration', 'Pesticide Resistance', 'Mutant Frequency', 'Body Condition', 'Fitness Senescence', 'Lifespan', 'Male Attractiveness', 'Mating Frequency', 'Mating Latency', 'Mating Success', 'Strength', 'Ejaculate Quality and Production', 'Extinction Rate', 'Offspring Viability', 'Reproductive Success')
#Obtain BF for all components
Hypotheses <- list()
BFs <- list()
Hypotheses[["Behavioural Plasticity"]] <- hypothesis(components.brms, "Intercept > 0") #Intercept in model, need to do it by itself
BFs[["Behavioural Plasticity"]] <- Hypotheses[["Behavioural Plasticity"]][["hypothesis"]][["Evid.Ratio"]]
for (i in BF.outcome.list){
Hypotheses[[i]] <- hypothesis(components.brms, paste("Intercept + Outcome",i," > 0", sep = ""))
BFs[[i]] <- Hypotheses[[i]][["hypothesis"]][["Evid.Ratio"]]
} #Loop for all fitness compoinents

fitness.component.predictions %>% cbind.data.frame(as.data.frame(BFs) %>% t() %>% as.data.frame() %>% `colnames<-`("BF")) %>% add_significance_stars2() %>% pander(split.cell = 40, split.table = Inf, digits = 2)
```
